State of the Practice for Lattice Boltzmann Method Software

### 2022-01-30 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
added new column into table 6

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{2.5cm}p{2cm}p{2cm}p{2cm} }
			\toprule
			Name & Our Ranking & Repository Stars & Repository Star Rank &
			Repository Watches \\
			\midrule
			ESPResSo & 1 & 145 & 2 & 19\\
			Ludwig & 2 & 27 & 8 & 6\\
			Palabos & 3 & 34 & 6 & GitLab\\
			OpenLB & 4 & No Git & No Git & No Git\\
			LUMA & 5 & 33 & 7 & 12\\
			pyLBM & 6 & 95 & 3 & 10\\
			DL\_MESO (LBE) & 7 & No Git & No Git & No Git \\
			Musubi & 8 & No Git & No Git & No Git \\
			Sailfish & 9 & 186 & 1 & 41\\
			waLBerla & 10 & 20 & 9 & GitLab\\
			laboetie & 11 & 4 & 13 & 5\\
			TCLB & 12 & 95 & 3 & 16\\
			MechSys & 13 & No Git & No Git & No Git\\
			lettuce & 14 & 48 & 4 & 5\\
			ESPResSo++ & 15 & 35 & 5 & 12\\
			MP-LABS & 16 & 12 & 11 & 2\\			
			SunlightLB & 17 & No Git & No Git & No Git\\
			LB3D & 18 & No Git & No Git & No Git\\			
			LIMBES & 19 & No Git & No Git & No Git\\
			LB2D-Prime & 20 & No Git & No Git & No Git\\		
			HemeLB & 21 & 12 & 11 & 12\\
			lbmpy & 22 &  11 & 12 & 2\\	
			LB3D-Prime & 23 & No Git & No Git & No Git\\	
			LatBo.jl & 24 & 17 & 10 & 8\\			
			\bottomrule
		\end{tabular}
		\caption{Repository Ranking Metrics} \label{repometrics}
	\end{center}
	\end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{1.25cm}p{1.75cm}p{1.75cm}p{1.75cm}p{1.75cm} }
			\toprule
			Name & Our Ranking & Repository Stars & Repository Star Rank &
			Repository Watches & Repository Watch Rank\\
			\midrule
			ESPResSo & 1 & 145 & 2 & 19& 2\\
			Ludwig & 2 & 27 & 8 & 6& 7\\
			Palabos & 3 & 34 & 6 & GitLab& GitLab\\
			OpenLB & 4 & No Git & No Git & No Git& No Git\\
			LUMA & 5 & 33 & 7 & 12& 4\\
			pyLBM & 6 & 95 & 3 & 10& 5\\
			DL\_MESO (LBE) & 7 & No Git & No Git & No Git & No Git\\
			Musubi & 8 & No Git & No Git & No Git & No Git\\
			Sailfish & 9 & 186 & 1 & 41& 1\\
			waLBerla & 10 & 20 & 9 & GitLab& GitLab\\
			laboetie & 11 & 4 & 13 & 5& 8\\
			TCLB & 12 & 95 & 3 & 16& 3\\
			MechSys & 13 & No Git & No Git & No Git& No Git\\
			lettuce & 14 & 48 & 4 & 5& 8\\
			ESPResSo++ & 15 & 35 & 5 & 12& 4\\
			MP-LABS & 16 & 12 & 11 & 2& 9\\			
			SunlightLB & 17 & No Git & No Git & No Git& No Git\\
			LB3D & 18 & No Git & No Git & No Git& No Git\\			
			LIMBES & 19 & No Git & No Git & No Git& No Git\\
			LB2D-Prime & 20 & No Git & No Git & No Git& No Git\\		
			HemeLB & 21 & 12 & 11 & 12& 4\\
			lbmpy & 22 &  11 & 12 & 2& 9\\	
			LB3D-Prime & 23 & No Git & No Git & No Git& No Git\\	
			LatBo.jl & 24 & 17 & 10 & 8& 6\\			
			\bottomrule
		\end{tabular}
		\caption{Repository Ranking Metrics} \label{repometrics}
	\end{center}
	\end{table}
